Explore resilience evi

### 2017-11-24 analysis/evi/explore_resilience.Rmd
add pdf

---
title: "Explore resilience evi"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 Aug"
output: 
  md_document:
    variant: markdown_github
---
```{r, echo=FALSE, message=FALSE}
require(knitr)
opts_chunk$set(fig.align='center', message = FALSE, warning = FALSE) 
```

>>>>

---
title: "Explore resilience evi"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 Aug"
output: pdf_document
---
```{r, echo=FALSE, message=FALSE}
require(knitr)
opts_chunk$set(fig.align='center', message = FALSE, warning = FALSE) 
```
